Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-04 paper.tex
update

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Figure \ref{parallel}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level. where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.

@@

To visually compare the results generated from two evaluation approaches, we demonstrate the differences of composition weighted graphs under two different methods. The Figure \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for comprehensive quality-aware and QoS-aware web service composition respectively. The two weighted graphs have exactly the same workflow structure, in which the different service vertex and edges are denoted in red for making a comparison.

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{} & Comprehensive-aware & QoS-aware &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$        &        1   &  1 &0\\ \cline{2-5} 
                    & $q(e_{s})$                    &     1      & 1& 0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$                     &    0.9167       & 0.75 & \\ \cline{2-5} 
                    &   $q(e_{s})$                    &   0.9630        & 0.9232 &\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$                   &    0.8333       & 0.75 &\\ \cline{2-5} 
                    &   $q(e_{s})$                    &    0.9608       &  0.8230 &\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$                      &    0.875       & 0.75 &\\ \cline{2-5} 
                    &  $q(e_{s})$                     &    0.9167       & 0.9090 &\\ \hline
\multicolumn{2}{|l|}{SM} &                     &           &  \\ \hline
\multicolumn{2}{|l|}{QoS} &        0.4915             &  0.4949         &  \\ \hline
\end{tabular}
\end{table}

@@

To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09. To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function. We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.

Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs. The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. Also, there is a fast convergence of the fitness value that be observed. That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.

We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}. In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks. However, there are some slight fluctuations over the generations, due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.

Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward. Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}. It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks. Additionally, we don't see too much trade-off from the QoS.

>>>>

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Fig. \ref{parallel}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level. where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which can be described in the Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.

@@

To visually compare the results generated from two evaluation approaches, we demonstrate the differences in the solutions of two composition weighted graphs under two different methods. The Fig. \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for(1) QoS-aware approach and $(2)$ Comprehensive quality-aware method and respectively. It can be observed that two composition weighted graphs have exactly the same workflow structure, in which the same service vertex and edges are different denoted in red. Meanwhile, we make a comparison of those different edges weights representing the quality of semantic matchmaking in Table \ref{comparisontable},as well as QoS. We can see edges obtain better semantic matchmaking quality with a reasonable trade-off in QoS

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Comparison of Composition Weighted Graphs}
\label{comparisontable}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{Quality criteria} & Weighted Graph $(1)$ & Weighted Graph $(2)$ &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
                    & $q(e_{s})$   &1        &1                       &0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
\multicolumn{2}{|l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
\end{tabular}
\end{table}

@@

To analyse the effectiveness of our approach, we will study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09. To further study the overall effectiveness of evaluation model and explore impacts of all involved components in the fitness function. We analysis all the performances of these components in the whole evolutionary process in Fig. \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.

Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs. The value plotted in the first column group ranges from 0 to 1 in Fig. \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. We also witnessed a fast convergence rate of the fitness value.

We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied from generation 0 to 99 in second and third column groups of Fig. \ref{exp_fitnessvalue}. In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks. However, there are some slight fluctuations over the generations.

Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the functional quality heads up. Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Fig. \ref{exp_fitnessvalue}. It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks. Additionally, we don't see too much trade-off from the QoS.
